Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-12 CAs_operads.tex
Petites modifs

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
 the left and the right members of the rewriting rules are trees
 belonging to $\Mag$.
\medbreak

Thanks to the partial completions presented in table
\ref{tab:cardinalities_completion_CAs}, we can compute the following 
first dimensions of $\CAs{\gamma}$. Table~\ref{tab:dimensions_CAs}
 shows the first dimensions of the
operads $\CAs{\gamma}$ for $\gamma \in [9]$.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccc}
        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
        & 35357670
        \\
        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
        & 1 & 1
        \\
        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
        14 & 15 & 16 & 17 & 18 & 19 & 20
        \\
        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
        %& 5778420 & 15882100 & 43837388 & 121507230
        \\
        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
        & 40392 & 131997 & 433782 & 1432696 & 4752857
        & 15829261
        %& 52905635 & 177395246
        \\
        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
        & 52598 & 180895 & 626862 & 2186504 & 7670138
        & 27041833
        %& 95764569
        \\
        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
        & 56966 & 199444 & 704140 & 2503914 & 8959699
        & 32236657
        %& 116551168
        \\
        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
        %& 124958386
        \\
        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
        %& 128082515
    \end{tabular}
    \medbreak

    \caption{\footnotesize
    The sequences of the cardinalities, arity by arity, of the
    dimensions of~$\CAs{\gamma}$.}
    \label{tab:dimensions_CAs}
\end{table}
\medbreak

>>>>

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$\left\{\Tfr_1, \Tfr_2\right\}$ which is not joinable, we recursively
try to find a completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
the left and the right members of the rewrite rules are trees
belonging to $\Mag$.
\medbreak

Thanks to the partial completions presented in
Table~\ref{tab:cardinalities_completion_CAs}, we can compute the
following first dimensions of $\CAs{\gamma}$.
Table~\ref{tab:dimensions_CAs} shows the first dimensions of the
operads $\CAs{\gamma}$ for $\gamma \in [9]$.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccc}
        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
        & 35357670
        \\
        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
        & 1 & 1
        \\
        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
        14 & 15 & 16 & 17 & 18 & 19 & 20
        \\
        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
        %& 5778420 & 15882100 & 43837388 & 121507230
        \\
        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
        & 40392 & 131997 & 433782 & 1432696 & 4752857
        & 15829261
        %& 52905635 & 177395246
        \\
        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
        & 52598 & 180895 & 626862 & 2186504 & 7670138
        & 27041833
        %& 95764569
        \\
        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
        & 56966 & 199444 & 704140 & 2503914 & 8959699
        & 32236657
        %& 116551168
        \\
        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
        %& 124958386
        \\
        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
        %& 128082515
    \end{tabular}
    \medbreak

    \caption{\footnotesize
    The sequences, arity by arity, of the dimensions of~$\CAs{\gamma}$.}
    \label{tab:dimensions_CAs}
\end{table}
\medbreak
